Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-10-26 manu-draft.Rmd
update k brevis figs and text with current data from CL

The increase in *K. brevis* from April to July to bloom concentrations exceeding 10,000 cells/L was an anomaly in 2021 that is not regularly observed in Tampa Bay.  The historical record from 1995 to present in Figure \@ref(fig:redtide)a shows the range of cell concentrations sampled in middle and lower Tampa Bay, with only a handful of years having median cell concentrations greater than 10,000 cells/L, notably 2005 and 2018. Median cell concentrations for most years were well below 1,000 cells/L.  The highest concentration of 17.6 million cells/L was observed in 2021, whereas only 2006 had a maximum observed concentration above 10 million cells/L [@Flaherty11].  Seasonally in 2021, bloom concentrations were not observed until the week of May 23, with concentrations peaking by the week of July 4th, after which concentrations declined (Figure \@ref(fig:redtide)b).  Cumulative rainfall and associated inflow from the main rivers entering Tampa Bay were below historical baseline values (1995 - 2020) in the months prior to the highest bloom concentrations (Figure \@ref(fig:redtide)c, d). This likely contributed to elevated salinity values in lower and middle Tampa Bay that created conditions favorable for *K. brevis* growth, in addition to the elevated nutrient concentrations from the Piney Point discharge.

>>>>

The increase in *K. brevis* from April to July to bloom concentrations exceeding 10,000 cells/L was an anomaly in 2021 that is not regularly observed in Tampa Bay.  The historical record from 1953 to present in Figure \@ref(fig:redtide)a shows cell concentrations sampled in middle and lower Tampa Bay between April and September, with only a handful of years having cell concentrations greater than 10,000 cells/L, notably 1963, 1971, 2005, 2018, and 2021. Median cell concentrations for most years were well below 1,000 cells/L. The highest concentration of 20 million cells/L was observed in 1971, whereas the second highest concentration of 17.6 million cells/L was observed in 2021. Seasonally in 2021, bloom concentrations were not observed until the week of May 23, with concentrations peaking by the week of July 4th, after which concentrations declined (Figure \@ref(fig:redtide)b).  Cumulative rainfall and associated inflow from the main rivers entering Tampa Bay were below historical values (1995 - 2020) in the months prior to the highest bloom concentrations (Figure \@ref(fig:redtide)c, d). This likely contributed to elevated salinity values in lower and middle Tampa Bay that created conditions favorable for *K. brevis* growth, in addition to the elevated nutrient concentrations from the Piney Point discharge.
